---
title: "Report"
author: "Madeline Tobias"
date: "`r Sys.Date()`"
output: pdf_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tinytex::install_tinytex()
```

In this analysis, I will be using a data set, titled player_data_standard, that refers to individual players in European soccer clubs and their current affiliation, as well as standard statistics related to their season highlights.  

```{r}
setwd("/home/rstudio/work/611")
getwd()
player_data_standard <- read.csv("source_data/player_data_standard.csv")

head(player_data_standard)
```

I will describe the meaning of the different columns. 

Player - Player name 
Nation - Abbreviations (2 variations) of the Nation where the player originates from 
Pos - Position 
League - League affiliation
Squad - Squad (or team) affiliation 
Age - Age of player
Born - Year born 
MP - Matches played
Starts - Number of starts during the regular season 
Min - Minutes Played 
X90s - Number of minutes / 90, ie number of 'full game' lengths played in total 
Gls - Goals scored 
Ast - Assisted goals 
G.A - Goals and assists 
G.PK - Non-penalty goals
PK - Peanalty kicks made
PKatt - Penalty kicks attempted
CrdY - Yellow Cards
CrdR - Red Cards
xG - Expected goals scored
npxG- Non-penalty expected goals scored
xAG - Expected assisted goals 
npxG.xAG
PrgC - Progressive Carries
PrgP - Progressive passes
PrgR - progressive receptions 
Gls.1
Ast.1
G.A.1
